Optimal (Multiway) Spatial Joins

### 2024-05-29 4.3.tex
4.3

First, we prove (1). For any $i \in [k-2]$, $r_i^*\in R_i^*$, and $h \in \cross_H(r_i^*)$, we will identify a unique tuple $\bm{t} \in \J(R_1,...,R_{k-2},H,V)$ such that $\bm{t}[k-1] = h$, and $\bm{t}[i]$ is the full rectangle of $r_i'$, whose top-slice is $r_i^*$. Let $\maxtop(r_i') = \ytop(B_\bm{t'})$ for some tuple $\bm{t'} \in \J(R_1',...,R_{k-2}')$. Let $\bm{t'} = (r'_1,...,r'_{k-2})$, and let $r_i$ be the full rectangle of $r_i'$ for $i \in [k-2]$. Since $h$ crosses $r_i^*$, and $B_\bm{t'} \subseteq r_i^*$, $h$ crosses $B_{\bm{t'}}$. Let $v$ be the segment $v_\vdash$ of $\gleft(\bm{t'})$. The intersection of $h$ and $v$ is a point on the left boundary of $B_{\bm{t'}}$, which means that $h\cap v \in B_{\bm{t'}} \subseteq \cap_{i = 1}^{k-2}r_i$. Therefore, $\bm{t} = (r_1,...,r_{k-2},h,v)\in \J(R_1,...,R_{k-2},H,V)$ is the desired tuple. As a result, $\sum_{i \in [k-2]}\sum_{r_i^*\in R_i^*} |\cross_H(r_i^*)| \leq \out$.

>>>>

First, we prove (1). For any $i \in [k-2]$, $r_i^*\in R_i^*$, and $h \in \cross_H(r_i^*)$, we will identify a unique tuple $\bm{t} \in \J(R_1,...,R_{k-2},H,V)$ such that $\bm{t}[k-1] = h$, and $\bm{t}[i]$ is the full rectangle of $r_i'$, whose top-slice is $r_i^*$. Let $\maxtop(r_i') = \ytop(B_\bm{t'})$ for some tuple $\bm{t'} \in \J(R_1',...,R_{k-2}')$. Let $\bm{t'} = (r'_1,...,r'_{k-2})$, and let $r_i$ be the full rectangle of $r_i'$ for $i \in [k-2]$. Since $h$ crosses $r_i^*$, and $B_\bm{t'} \subseteq r_i^*$, $h$ crosses $B_{\bm{t'}}$. Let $v$ be the segment $v_\vdash$ of $\gleft(\bm{t'})$. The intersection of $h$ and $v$ is a point on the left boundary of $B_{\bm{t'}}$, which means that $h\cap v \in B_{\bm{t'}} \subseteq \cap_{i = 1}^{k-2}r_i$. Therefore, $\bm{t} = (r_1,...,r_{k-2},h,v)\in \J(R_1,...,R_{k-2},H,V)$ is the desired tuple, and we have $\sum_{i \in [k-2]}\sum_{r_i^*\in R_i^*} |\cross_H(r_i^*)| \leq \out$.

Next, we prove (2). Let $r' = [x_1,x_2]\times [y_1,y_2]$, and $r^* = [x_1,x_2] \times [y_1,\maxtop(r')]$. Since $\gbot(\bm{t}) = r'$, $\dcross_H(\bm{t})$ contains exactly every segment $h \in H$ that crosses the rectangle $[x_1,x_2]\times [y_1, \ytop(B_\bm{t})]$, where $\ytop(B_{\bm{t}})\leq \maxtop(r')$. Therefore, $\dcross_H(\bm{t})$ $\subseteq \cross_H(r^*)$. Furthermore, if the (horizontal) segments of $\cross_H(r^*)$ are sorted in ascending order of y-coordinate, then $\dcross_H(\bm{t})$ includes a prefix of the sorted order.
